\newpage
\phantomsection
\thispagestyle{plain}

\vspace*{\fill}
\begingroup
\centering

\begin{LARGE}

\textbsi{To Chelsea}

\textbsi{(the blonde science nerd from heaven)}

\end{LARGE}

\endgroup
\vspace*{\fill}

\newpage
\phantomsection
\altchapter{Acknowledgments}

\thispagestyle{plain}

It is a pleasure to thank the many people that made this thesis possible.

I want to thank my advisors, Dr. Ross Mitchell and Dr. Mario Costa Sousa, for suggesting that I tackle such an interesting problem. They provided a continuous stream of encouragement, valuable input, and financial support throughout the development of the research in this thesis. For this I will always be grateful.

I  want to thank my co-author and lab mate Jeff Packer. Jeff generously volunteered his spare time to implement the GPU narrow band algorithm, which made several of the experiments in this thesis possible.

I want to thank my fellow students in the graphics, visualization, and medical imaging informatics labs -- Adam Runions, Sonny Chan, Eric Penner, Matt Tobiasz, and Sean Lynch -- for being so inspirational and brilliant. I'd like to thank Adam and Sean for proof-reading a very early draft of my High Performance Graphics paper and providing valuable and detailed feedback. I'd especially like to thank Sean for always taking time to go for a coffee, talk, and otherwise procrastinate with me.

I want to thank Dr.\ John Owens for putting his entire graphics architecture course on YouTube, for his valuable career and writing advice, for always pushing me to get my work published, and for being such an inspirational and friendly character. I want to thank Dr.\ Fredo Durand for his excellent notes on writing and Dr.\ Tamara Munzner for her excellent  advice on doing visualization research. I want to thank Dr.\ Mark Harris and the many other contributors on the CUDA forums for sharing their wealth of knowledge and experience about CUDA programming.

I want to thank Dr.\ Alan Evans for making the BrainWeb phantom MRI data available online. I also want to thank Dr.\ Mark Harris, Dr.\ John Owens, Shubho Sengupta, Stanley Tseng, Yao Zhang, Andrew Davidson, and Nadatur Satish for making their stream compaction code available through the expertly designed open-source CUDPP library. As an aside, I'd like to thank Anjul Patney for being a such a friendly face at conferences, Shubho Sengupta for graciously welcoming me into his home when I visited the University of California at Davis, and Andrew for generously giving me a lift to the airport during the same visit.

\thispagestyle{plain}

I want to thank Brian Kretzler, Greg Smith, Jason Cohen, Neall Verheyde, Nigel Brooke, Mark James, Paul Stark, Mike Hughes, and the many other inspirational and brilliant individuals I met while interning at NVIDIA and Radical Entertainment for teaching me so much about large-scale software development. 

On a personal note, I want to thank some particularly inspirational friends: Graham Evans, Justin Kangarloo, Louise Chong, Norrie Meth, Jenna Meth, Leah Meth, Marcus Sixta, Raj Trivedi, and Samir Khatani. This diverse group of friends has in common a positive spirit, a belief in themselves, and an unshakable dedication to their goals. I want to thank these friends for being such a continued source of inspiration in my life.

I want to thank my best friend and mentor Rob Faust. Rob was the most supportive friend imaginable throughout the development of my research. Rob always gave me unique, friendly, and hilarious guidance in all the areas of my life -- academic and otherwise. Rob is a truly inspirational character and I will always appreciate the presence of him and our confetti cannon in my life. \emph{MJ Cole on the remix!}

I especially want to thank the Leishman family -- Don, Lorraine, Savannah, and Sara -- for their unwavering support for the entire time I've known them. I want to thank them for welcoming me into their home and always being happy to have me study at their kitchen table. I can honestly say that all the good ideas in this thesis were born at that kitchen table.

I want to thank one particular member of the Leishman family more than anyone: my loving, supportive, absolute sweetheart, blonde science nerd from heaven girlfriend Chelsea. I want to thank Chelsea for her inspirational positivitiy, dedication, and utterly hilarious sense of humour. I want to thank her for being such a keener at school so we could study together so much, for being cool about it when I needed to stay up really late to finish something, for always believing in me, and for being an otherwise perfect partner-in-crime. I dedicate this thesis to her.

\thispagestyle{plain}

