\phantomsection
\fancyhead[RO,LE]{\thepage}
\fancyfoot{} 
\chapter{Publications}
\label{app:publications}

The research in this thesis makes the following contributions.

\section{Refereed Conference Papers}

\begin{noindent}Mike Roberts, Jeff Packer, Mario Costa Sousa, Joseph Ross Mitchell. A work-efficient GPU algorithm for level set segmentation. In \emph{ACM SIGGRAPH/Eurographics Conference on High Performance Graphics 2010 (HPG '10)}. pages 123--132, June 2010.\end{noindent}

\section{Refereed Oral Presentations}

\begin{noindent}Mike Roberts, Jeff Packer, Mario Costa Sousa, Joseph Ross Mitchell. A work-efficient GPU algorithm for level set segmentation. Oral presentation at \emph{Nvidia GPU Technology Conference Research Summit 2010 (GTC '10)}. September 2010.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Eric Penner, Jeff Packer, Mario Costa Sousa, Joseph Ross Mitchell. Advanced medical volume rendering and segmentation on the GPU. Oral presentation at \emph{Nvidia GPU Technology Conference Research Summit 2010 (GTC '10)}. September 2010.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Jeff Packer, Mario Costa Sousa, Joseph Ross Mitchell. Level set segmentation of large medical data sets on modern graphics hardware. In \emph{10th Annual Alberta Biomedical Engineering Conference 2009}. page 24. October 2009.\end{noindent}

\section{Refereed Posters}

\begin{noindent}Mike Roberts, Jeff Packer, Mario Costa Sousa, Joseph Ross Mitchell. Interactive 3D level set segmentation on modern graphics hardware. Oral presentation at \emph{Radiological Society of North America Annual Meeting 2010 (RSNA '10)}. November 2010.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Mario Costa Sousa, Joseph Ross Mitchell. A work-efficient GPU algorithm for level set segmentation. Poster at \emph{ACM SIGGRAPH 2010}. July 2010. \textbf{ACM SIGGRAPH Student Research Competition Semi-Finalist}.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Jeff Packer, Mario Costa Sousa, Joseph Ross Mitchell. Using desktop graphics processors in diagnostic medicine. Poster at \emph{University of Calgary Graduate Conference 2010}. May 2010. \textbf{Natural Sciences and Engineering Research Council of Canada (NSERC) Best Poster Award}.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Jeff Packer, Mario Costa Sousa, J. Ross Mitchell. Level set segmentation of large medical data sets on modern graphics hardware. Poster at \emph{25th Anniversary Alberta Cancer Research Institute Research Meeting 2009}. November 2009.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Jeff Packer, J. Ross Mitchell, Mario Costa Sousa. CUDA-accelerated sparse-field level set segmentation of large medical data sets on modern graphics hardware. Poster at \emph{Nvidia GPU Technology Conference Research Summit 2009 (GTC '09)}. September 2009.\end{noindent}

\section{Patents}

\begin{noindent}Mike Roberts, Joseph Ross Mitchell, Mario Costa Sousa. Parallel process for level set segmentation of volume data. \emph{United States Patent filed on June 7th, 2010}.\end{noindent}

\bigskip

\begin{noindent}Mike Roberts, Joseph Ross Mitchell, Mario Costa Sousa. Level set segmentation of volume data. \emph{United States Provisional Patent filed on September 25th, 2009}.\end{noindent}

